\section{Experience}

\textbf{Software Development Intern, Inigo \hfill (January 2026 - May 2026)}

\begin{itemize}[noitemsep]
    \item Used Python, Flask, Postgres, Typescript, React, and Tanstack Router to develop a finance/invoicing platform.
    \item Documented an undocumented codebase for greater usability and developer productivity.
\end{itemize}

\textbf{Summer of Nix Fellow, NixOS Foundation \hfill (June 2025 - September 2025)}

\begin{itemize}[noitemsep]
    \item Used Nix, NixOS, Rust, Python, and OCaml to package 50+ programs and modules for clients across the E.U.
    % \item Communicated with a team across 4 continents to develop using Open-Source platforms and methods.
\end{itemize}

\textbf{IT Support Intern Team Lead, Carroll County Public Schools \hfill (March 2023 - August 2025)}

\begin{itemize}[noitemsep]
    \item Managed a team of 6 interns across three buildings over the span of three years. Hired interns each year.
    \item Wrote PowerShell scripts to simplify software delivery process for district, saving hundreds of man-hours.
    \item Deployed 1,200+ Chromebooks and 80+ AV systems; conducted professional development training to faculty and staff.
    \item Livestreamed, recorded, and managed AV for graduations, board meetings, talent shows, and more.
\end{itemize}

\ifnum\pdfstrcmp{\jobname}{cv}=0
    \textbf{Contributing Technical Writer, StorageReview.com \hfill (June 2021 - December 2021)}

    \begin{itemize}[noitemsep]
        \item Wrote 7 articles on networking equipment, enterprise and consumer storage options, and Homelab technologies.
        \item Benchmarked, tested, and reviewed enterprise and consumer server hosting software.
    \end{itemize}
\fi

\textbf{Systems Administrator Intern, AlthaTechnology \hfill (March 2020 - August 2021)}

\begin{itemize}[noitemsep]
    \item Designed and implemented a distributed storage system serving up to 30 servers with 10Gb/s fiber network.
    \item Implemented distributed and highly available compute layer using Docker Swarm, reducing costs by \$300/month.
\end{itemize}
