\section{Projects and Activities}

\textbf{The Ridge Podcast}, NextJS, React, Flask, Cloudflare R2, SCSS, Docker, REST APIs \hfill \href{https://theridgepodcast.com}{Website}

\begin{itemize}[noitemsep]
    \item Developed a custom podcast CMS to serve 500+ daily listeners with 99\% uptime using a global CDN system.
    \item Interviewed 100+ politicians, historians, veterans, musicians, journalists, writers, teachers, and more.
\end{itemize}

\textbf{The Harvard Crimson Tech Board}, Django, React, Cloudflare R2, GraphQL \hfill \href{https://thecrimson.com}{Website}

\begin{itemize}[noitemsep]
    \item Migrated site serving 21 annual million viewers from Amazon S3 to Cloudflare R2, saving \$400/month.
    \item Debugged cache invalidation issues, developed interactive article editor, ArchieML parser.
\end{itemize}

\textbf{Dracula Tmux}, Bash, REST APIs, Open-Source \hfill \href{https://github.com/dracula/tmux}{800+ GitHub Stars}
\begin{itemize}[noitemsep]
    \item Maintainer for a popular Open-Source modular tmux plugin for Linux and *BSD systems.
    \item Developed statuses for Kubernetes, Git, Terraform, Weather, GPU/RAM/CPU utilization, and Blood Glucose levels.
\end{itemize}

\textbf{NixOS Linux/Nixpkgs Maintainer}, Nix, Python, Rust, Open-Source

\begin{itemize}[noitemsep]
    \item Serve on the MacOS Darwin and NGI dev teams. Maintain 200+ packages. Reviewed 2100+ PRs. 200+ PRs merged.
\end{itemize}

\textbf{Homelab, Home Networking, and Self-Hosting}, Docker, ZFS, NFS, Proxmox, Networking

\begin{itemize}[noitemsep]
    \item Maintain a multi-architecture web hosting fleet to host sites with 2K+ daily active users at a 99\% uptime.
    \item Hardware includes Dell Poweredge R320, Cisco 3750G L3 Switch, and managed WiFi Access Points.
\end{itemize}
